### 2017-01-02 paper/evaluation.tex
Updated maven version

To run our experiments, we used a \emph{Core i7-4790} (3.60 GHz) Intel
processor machine with 8 virtual CPUs (4 cores with 2 native threads
each) and 16GB of memory, running \emph{Ubuntu 14.04 LTS Trusty Tahr}
(64-bit version). Software settings include \Comment{the Linux
\emph{sysstat} package to measure performance, }\emph{git} to fetch
subjects, \emph{Java 8} and \emph{Maven 3} to build and test subjects,
and \emph{Python 3.4} to run our evaluation scripts. For replication,
all source artifacts are publicly available at \Fix{create gh-pages},
including supporting scripts (\eg, the script that test subjects and
generates the raw data), the full list of projects, and a
\emph{Vagrantfile} to emulate our hardware and all software
dependencies.

>>>>

To run our experiments, we used a \emph{Core i7-4790} (3.60 GHz) Intel
processor machine with 8 virtual CPUs (4 cores with 2 native threads
each) and 16GB of memory, running \emph{Ubuntu 14.04 LTS Trusty Tahr}
(64-bit version). Software settings include \Comment{the Linux
\emph{sysstat} package to measure performance, }\emph{git} to fetch
subjects, \emph{Java 8} and \emph{Maven 3.3.9} to build and test subjects,
and \emph{Python 3.4} to run our evaluation scripts. For replication,
all source artifacts are publicly available at \Fix{create gh-pages},
including supporting scripts (\eg, the script that test subjects and
generates the raw data), the full list of projects, and a
\emph{Vagrantfile} to emulate our hardware and all software
dependencies.
